### 2015-06-10 LOI/inc2.tex
Fixed the header for the pre-proposal

  %  \end{enumerate}
  %   
\setlength{\parindent}{0cm} 
{\bf Title of Pre-application:}  Science-driven Data Management for multi-tiered storage\par
{\bf Principal Investigator:} Scott Klasky, Group Leader, ORNL, 854-241-9980, klasky@ornl.gov \par
{\bf Funding Opportunity Announcement Number: DE-FOA-0001338} \par
 \vskip 0.0 in
\hskip -0.08in
\begin{tabular} {ll}
 \multicolumn{2}{l}{\bf Co-PIs and Key/Senior Personnel}\\
Hasan Abbasi, ORNL  & Mark Ainsworth, ORNL JFA, Brown University \\
Matthew Curry, SNL & Qing  Liu, ORNL \\
Jay Lofstead, ORNL & Kimmy Mu, ORNL \\
Carlos Malzahn, U. Cal. Santa Cruz & Manish Parashar, Rutgers University, ORNL JFA \\
Feiyi Wang, ORNL & Lee Ward, SNL
\end{tabular}

>>>>

  %  \end{enumerate}
  %   
\setlength{\parindent}{0cm} 
{\bf Title of Pre-application:}  Science-driven Data Management for multi-tiered storage\par
{\bf Principal Investigator:} Scott Klasky, Group Leader, ORNL, 854-241-9980, klasky@ornl.gov \par
{\bf Laboratory Announcement Number: LAB 15-1338, Funding/year: \$1.25M} \par
 \vskip 0.0 in
\hskip -0.08in
\begin{tabular} {ll}
 \multicolumn{2}{l}{\bf Co-PIs and Key/Senior Personnel}\\
Hasan Abbasi, ORNL  & Mark Ainsworth, ORNL JFA, Brown University \\
Matthew Curry, SNL & Qing  Liu, ORNL \\
Jay Lofstead, ORNL & Kimmy Mu, ORNL \\
Carlos Malzahn, U. Cal. Santa Cruz & Manish Parashar, Rutgers University, ORNL JFA \\
Feiyi Wang, ORNL & Lee Ward, SNL
\end{tabular}
